---
title: "HW 2"
author: "Tianqi Luo"
date: "`r Sys.Date()`"
output: html_document
urlcolor: "blue"
params:
  solutions: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo       = params$solutions, 
                      eval       = params$solutions,
                      fig.align  = "center",
                      fig.height = 3, 
                      fig.width  = 5)
```

## Problem 1##

### 1 ###

**Read the data**
```{r}
library(tidyverse)
library(lubridate)
cw = read_csv("../data/civil_war.csv")
head(cw)
```



### 2 ###

```{r}
year_regex = str_c(1861:1865, collapse = "|")
year_regex
```

```{r}
cw %>%
  mutate(year_count = str_count(Date, year_regex)) ->
  cw_year_count

head(cw_year_count)
```

### 3 ###


```{r}
month.name
```

```{r}
month_regex = str_c(month.name, collapse = "|")
month_regex
```

```{r}
cw_year_count %>%
  mutate(month_count = str_count(Date, month_regex)) ->
  cw_year_month_count

head(cw_year_month_count)
```

### 4 ###

```{r}
cw_year_month_count %>%
  mutate(multiple_days = str_detect(Date, "-")) ->
  cw_multiple_days

head(cw_multiple_days)
```

### 5 ###

**One day**
```{r}
cw_multiple_days %>%
  filter(multiple_days == FALSE) ->
  cw_one_day

head(cw_one_day)
```

**Multiple days one month**
```{r}
cw_multiple_days %>%
  filter(multiple_days == TRUE) %>%
  filter(month_count == 1) ->
  cw_multiple_days_one_month

head(cw_multiple_days_one_month)
```

**Multiple months**

```{r}
cw_multiple_days %>%
  filter(multiple_days == TRUE) %>%
  filter(month_count != 1) %>%
  filter(year_count == 1) ->
  cw_multiple_months_one_year

head(cw_multiple_months_one_year)
```

**Multiple years**
```{r}
cw_multiple_days %>%
  filter(multiple_days == TRUE) %>%
  filter(year_count != 1) ->
  cw_multiple_years

head(cw_multiple_years)
```


### 6 ###

```{r}
cw_one_day %>%
  separate(Date, into = c("Start", "End"), sep = "-") %>%
  mutate(Start = mdy(Start)) %>%
  mutate(End = Start) %>%
  dplyr:: select(Battle, State, Start, End, CWSAC, Outcome)-> tidy_one_day

head(tidy_one_day)
```

   
**Tidy the multiple days one month data**
```{r}
cw_multiple_days_one_month %>%
  separate(Date, into = c("StartMonthDay", "EndDayYear"), sep = "-") %>%
  separate(StartMonthDay, into = c("Month", "StartDay")) %>%
  separate(EndDayYear, into = c("EndDay", "Year")) %>%
  mutate(Start = paste(Month, StartDay, Year), End = paste(Month, EndDay, Year)) %>%
  mutate(Start = mdy(Start), End = mdy(End)) %>%
  dplyr:: select(Battle, State, Start, End, CWSAC, Outcome)->
  tidy_days_one_month

head(tidy_days_one_month)
```

**Tidy the multiple days multiple months data**
```{r}
cw_multiple_months_one_year %>%
  separate(Date, into = c("StartMonthStartDay", "EndMonthEndDayYear"), sep = "-") %>%
  separate(EndMonthEndDayYear, into = c("EndMonthEndDay", "Year"), sep = ",") %>%
  mutate(Start = paste(StartMonthStartDay, Year), End = paste(EndMonthEndDay, Year)) %>%
  mutate(Start = mdy(Start), End = mdy(End)) %>%
  dplyr:: select(Battle, State, Start, End, CWSAC, Outcome)->
  tidy_months_one_year

head(tidy_months_one_year)
```

**Tidy the multiple years**
```{r}
cw_multiple_years %>%
  separate(Date, into = c("Start", "End"), sep = "-") %>%
  mutate(Start = mdy(Start), End = mdy(End)) %>%
  dplyr:: select(Battle, State, Start, End, CWSAC, Outcome)->
  tidy_years

head(tidy_years)
```

### 7 ###

**Combine all the data into one**
```{r}
final_cw = rbind(tidy_one_day, tidy_days_one_month, tidy_months_one_year, tidy_years)

head(final_cw)
```

### 8 ###
```{r}
final_cw %>%
  mutate(Days = End - Start) ->
  final_cw_duration

final_cw_duration %>%
  filter(Days == max(Days)) %>%
  dplyr::select(Battle, Days)
  
```

**The longest battle is Siege of Port Hudson, it lasted for 49 days**

### 9 ###
```{r}
ggplot(final_cw_duration, aes(x = as.factor(CWSAC), y = Days)) + 
  geom_boxplot() + 
  geom_smooth(method = "lm", formula = y ~ as.factor(x), se = F) +
  #scale_y_log10() + 
  xlab("Significance") + 
  ylab("Duration") 
```

**We can see there is indeedn an association between the duration and the significance of the battle. As the significance gets greater, the battles tend to last longer**

### 10 ###

**Replace all the state name with parentheses with just the names**
```{r}
final_cw_duration %>%
  mutate(State = str_replace(State, "\\s*\\([^\\)]+\\)", "")) -> tidy_state_duration

head(tidy_state_duration)
```

**Create a data counting the number of apperances of the states**
```{r}
tidy_state_duration %>%
  count(State) ->tidy_cw_duration

tidy_cw_duration
```


**Filter the items with apperances more than 2**
```{r}
tidy_cw_duration %>%
  filter(n > 2) ->
  tidy_cw_duration_over_2

head(tidy_cw_duration_over_2)
```

**Use left_join to merge the count of states with the original dataset**
```{r}
state_count = left_join(tidy_cw_duration_over_2, tidy_state_duration, by = "State")

head(state_count)
```

**Create the graph, use fct_reorder to arrange the rank of the states**
```{r}
ggplot(state_count, aes(x = fct_reorder(State, Start) , y = Start)) + 
  geom_boxplot() + 
  coord_flip() + 
  xlab("State") + 
  ylab("Start Date")
```





