---
title: "HW 3"
author: "Tianqi Luo"
date: "`r Sys.Date()`"
output: html_document
urlcolor: "blue"
params:
  solutions: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo       = params$solutions, 
                      eval       = params$solutions,
                      fig.align  = "center",
                      fig.height = 3, 
                      fig.width  = 5)
```

## Question: Lists ##

### 1 ###

**Read the lists in**
```{r}
fitPoly = readRDS("../data/fpout.RDS")
```

### 2 ###

**Extract the names**
```{r}
names(fitPoly)
```

### 3 ###

**Remove the variable disploscores**
```{r}
fitPoly$diploscores = NULL

names(fitPoly)
```

### 4 ###

```{r}
library(tidyverse)
fitPoly$scores %>%
  mutate(PosteriorMean = 0* P0 + 1 * P1 + 2* P2 + 3 * P3 + 4* P4 + 5 * P5 + 6 * P6) -> tidy_fitpoly

head(tidy_fitpoly) %>%
  select(PosteriorMean)
```

**Add the posterior mean as a new variable in the scores data frame**
```{r}
fitPoly$scores = tidy_fitpoly

head(fitPoly$scores)
```

### 5 ###

```{r}
col_means = colMeans(fitPoly$scores[c("P0", "P1", "P2", "P3", "P4", "P5", "P6")])

col_means
```

**Attach the col_means variable to the dataframe**
```{r}
fitPoly$col_means = col_means
head(fitPoly$col_means)
```


### 6 ###

**First Method**
```{r}
fitPoly$time
```


**Second Method**
```{r}
fitPoly["time"]
```

**Third Method**
```{r}
names(fitPoly)
fitPoly[5]
```

## Question: For Loops ##

**Write the function using if else statements and for loop**
```{r}
calcn = function(x, n) {
  if(n>=1 & n <= 3) 
  {  x[n] = x[n]
    
  }
  else {
    for (i in 4:n) {
      x[i] = x[i-1] + (abs(x[i-2] - x[i-3]))/2
    }
    
  }
  return(x[n])
}
```



### Evaluate functions ###

```{r}
calcn(x = c(11, 1, 13), n = 1000)
calcn(x = c(11, 1, 13), n = 1)
calcn(x = c(7, 3, 20), n = 8)
```


### Question: Lists and For-Loops ###

```{r}
x = rnorm(n = 10, mean = 0, sd = 1)
tout = t.test(x)
```


### 1 ###

**Write the function in for loop to do the t-test 1000 times**
```{r}
set.seed(4744469)
x = list()
tlist = list()
for(i in 1:1000) { 
  x[i] = list(rnorm(10, 0, 1))
  tlist[i] = list(t.test(x[[i]]))
}
```



### 2 ###

**Extract the p-values from these 1000 t-tests into the variable p_values**
```{r}
p_values = vector("numeric", 1000)

for(i in 1:1000) {
  p_values[i] = tlist[[i]]$p.value
}
```

```{r}
head(p_values)
```


### Challenge ###

**Create a data frame with variable p-values**
```{r}
qq = data.frame(p_values)
```

**Mutate a the variable p as a scaled variable from 1 to 1000 and create a new dataframe with the p-values**
```{r}
qq %>%
  mutate(p = (1:1000)/1000 - 0.5/1000, p_values = sort(p_values)) ->
  qq_tidy

head(qq_tidy)
```

**Use ggplot to draw the dataframe using geom_point and geom_abline**
```{r}
ggplot(qq_tidy, aes(x = p, y = p_values)) + 
  geom_point() + 
  geom_abline(color = "red", linetype = 2) + 
  theme_bw() + 
  xlab("theoretical") + 
  ylab("sample")
```

**We can see that the p-values indeed follow the uniform distribution**


