
## Stat 613 HW 4 ##

## Tianqi Luo ##


## Question: Estate Data ##

### (1) ###

**Read data into Rmarkdown**
```{r message = FALSE}
library(tidyverse)
estate = read_csv("../data/estate.csv")

head(estate)
```

### (2) ###

```{r}
library(purrr)
```

**Write a function to test if the variable is binary**
```{r}
binary = function(x) {
  if (length(unique(x)) == 2){
    return("Binary")
    }
  
  else
    {return ("Not binary")}
}
```

**Write the map function to apply the function to the data**
```{r}
head(map(estate, binary))
```


### (3) ###




**Rewrite the function**
```{r}
head(estate %>%
  split(.$Style) %>%
  map(~lm(Price ~ Area, data = .)))
```

## Question: purrr ##

### (1) ###

**The code is used to generate 5 random samples in a normal distribution with mean 0 for varying standard deviations, the standard deviations range from 1 to 10.**

### (2) ###

**Write a function that generates x random samples from a normal distribution with mean = 10 and variance = 1, use the replicate function to repeat 1000 times**

```{r}
library(ggplot2)
norm_func = function(x) {
  sample = replicate(1000, {mean(rnorm(x, 10, 1))})
  norm_dat = data.frame(rep(x, 1000), sample)
  return(norm_dat)
}
```


**Use the map function to apply the function for all sample sizes, merge the dataframes**
```{r}
samples = map(c(1, 10, 50, 100, 500, 1000), norm_func)
samples_df = bind_rows(samples)

head(samples_df)
```

**Tidy the dataframe**
```{r}
samples_df %>%
  rename("n" = 1) %>%
  mutate(n = as.factor(n)) ->
  tidy_samples

head(tidy_samples)
```


**Draw a boxplot with the sample sizes the samples**
```{r}
ggplot(tidy_samples, aes(x = n, y = sample)) + 
  geom_boxplot() + 
  theme_bw()
```

**We can see as the samples sizes get larger, the sample mean gets closer to the distribution mean 10. When the sample sizes are super large(1000), they're almost entirely equal.**


## File Reading ##

**(1)**

**Make a list of the files from the gapminder folder**
```{r}
country_list = list.files("../data/gapminder")

head(country_list)
```

**Write a function using for loop to extract all the files into gaplist, use paste to change the directory by looping through the country list**
```{r message = FALSE}
gaplist = list()
link = vector("character", length(country_list))

for(i in 1: length(country_list)) {
  link[i] = paste("../data/gapminder", country_list[i], sep = "/")
  gaplist[[i]] = read_csv(link[i])
}
```

```{r}
head(gaplist)
```

### 3 ###

**Merge all the gaplist dataframes**
```{r}
all_gaplist = bind_rows(gaplist)

head(all_gaplist)
```




## Challenge ##

**Write a function by creating a sequence from 1 to x, loop through every single value to find the remainder with every value in the sequence. If the number of reminder is 2, then it is a prime, then remove the NA and return the vector.**

```{r}
get_prime = function(x) {
  prime = vector()
  sequence = seq(1:x)
  for(i in 1:x) {
  if(length(which(sequence[i] %% sequence[1:i] == 0)) == 2) {
   prime[i] = sequence[i]   
  }
  }
  prime = prime[which(prime != "NA")]
  return(prime)
}
```


**Test it on the values**
```{r}
get_prime(1)
get_prime(2)
get_prime(10)
get_prime(23)
```




