---
title: "Midterm 1 (40 pts)"
author: "Tianqi Luo"
date: "`r Sys.Date()`"
output: html_document
urlcolor: "blue"
params:
  solutions: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo       = params$solutions, 
                      eval       = params$solutions,
                      fig.align  = "center",
                      fig.height = 3, 
                      fig.width  = 5)
```

```{r, message = FALSE}
library(tidyverse)
```


## Question 1: Simulation Output ##


### 1 ###
```{r}
item_list = list.files("../data/fp_fits")
head(item_list)
```

**Use a for loop and paste function to read all of the data respectively in fplist**
```{r}
fplist = list()
link = vector("character", length(item_list))

for(i in 1: length(link)) {
  link[i] = paste("../data/fp_fits", item_list[i], sep = "/")
  fplist[[i]] = readRDS(link[i])
}
```



### 2 ###

```{r}
library(purrr)
```

**Write a function to extract the elapsed variable**
```{r}
elapsed_func = function(x) {
  elapsed = fplist[[x]]$time[[3]]
  return(elapsed)
}
```

**Use map function to create a list with elapsed variable for every data, then unlist the list**
```{r}
elapsed = unlist(map(seq(1,20), elapsed_func))
elapsed
```

### 3 ### 

```{r}
names(fplist[[1]]$scores)
```

**Write a function to calculate the means of P0 - P6 (The 5th column all the way to the 11th column)
```{r}
means_func = function(x) {
  means = colMeans(fplist[[x]]$scores[5:11])
  return(means)
}
```

**Use the map function to do it for every single data**
```{r}
means_total = map(seq(1,20), means_func)

means_total[[1]]
```



## Earthquakes: Dates ##

### 1 ###

**Read the data**
```{r message = FALSE}
eqbig = read_csv("../data/eqbig.csv")

head(eqbig)
```

### 2 ###

**Combine the Year with the Date variable by paste, then use wday to display the weekday**
```{r}
library(lubridate)
eqbig %>%
  mutate(NewDate = mdy(paste(Date, Year))) %>%
  mutate(Weekday = wday(NewDate, label = TRUE)) %>%
  group_by(Weekday) ->
  

  eqbig_tidy
  
```

```{r}
head(eqbig_tidy)
```

**Recode the weekday variable**
```{r}
eqbig_tidy$Weekday = recode_factor(eqbig_tidy$Weekday, "Sun" = "Sunday", "Mon" = "Monday", "Tue" = "Tuesday", "Wed" = "Wednesday", "Thu" = "Thursday", "Fri" = "Friday", "Sat" = "Saturday")
```


```{r}
head(eqbig_tidy)
```


**Plot the Magnitude with the Weekdays**
```{r}
library(ggplot2)
ggplot(eqbig_tidy, aes(x = Weekday, y = Magnitude)) + 
  geom_point() + 
  theme_bw() + 
  xlab("Day of the Week")
```



## Lists / Vectors ##

```{r, echo = TRUE, eval = TRUE}
ohio_state <- list(established = 1870,
                   nobel = tribble(~name,            ~year, ~field,
                                   ## --------------\------\-------
                                   "Leon Cooper",    1972,  "Physics",
                                   "Paul Flory",     1974,  "Chemistry",
                                   "William Fowler", 1983,  "Physics",
                                   "Kenneth Wilson", 1982,  "Physics"),
                   championship = tribble(~Year, ~Record, ~Bowl,
                                          1942,  "9–1",   NA,
                                          1954,	 "10–0",  "Rose Bowl",
                                          1957,	 "9–1",   "Rose Bowl",
                                          1961,	 "8–1",	NA,
                                          1968,	 "10–0",  "Rose Bowl",
                                          1970,	 "9–1",   "Rose Bowl",
                                          2002,	 "14–0",  "Fiesta Bowl",
                                          2014,	 "14–1",  "Sugar Bowl"),
                   song = c("In old Ohio there's a team",
                            "That's known throughout the land",
                            "Eleven warriors brave and bold",
                            "Whose fame will ever stand",
                            "And when that ball goes over,",
                            "Our cheers will reach the sky",
                            "Ohio Field will hear again",
                            "The Buckeye Battle Cry!"),
                   location = "Columbus, Ohio"
                   )
```

### 1 ###
```{r}
head(ohio_state)
```

**Separate the Record into variables Win and Loss**
```{r}
ohio_state$championship %>%
  separate(Record, into = c("Win", "Loss")) ->
  championship
```

**Change the dataframe from the list into the new one**
```{r}
ohio_state$championship = championship
```

```{r}
ohio_state$championship
```

### 2 ###

**First way**
```{r}
ohio_state$established
```

**Second way**
```{r}
ohio_state[["established"]]
```

**Third way, using the numeric index**
```{r}
names(ohio_state)
ohio_state[[1]]
```

## Iteration Challenge ##

```{r}
add_val = function(x) {
  if( x %% 1 != 0) {
    stop("n needs to be an integer")
  }
  else if( x < 0) {
    stop("n needs to be positive")
  }
  else {
  val = vector("numeric", x)
  val[1] = 2
  for(i in 1: x) {
    if(val[i] %% 6 == 0) {
      val[i + 1] = val[i] -1
    }
    else if(val [i] %% 2 == 0) {
      val[i + 1] = val[i] + 3
    
    }
    else if(val[i] %% 3 == 0) {
      val[i + 1] = val[i] + 2
    }
    else if(val[i] < 0) {
      stop("n needs to be positive")
    }
    else if(val[i] %% 1 != 0) {
      stop("n needs to be an integer")
    }
    else{
      val[i + 1] = val[i] - 1
    }
  }
    
  }
  return(val[x])
}

```


**Evaluate**
```{r error = TRUE}
add_val(-1)
```

```{r error = TRUE}
add_val(3.5)
```

```{r}
add_val(1)
add_val(2)
add_val(3)
add_val(4)
add_val(5)
add_val(100)
```
















